\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-09 fully-abstract-comp/popl2019/paper.tex
typos and removed todos

\todo[inline]{Describe $H^\mathrm{code,\square}_\sigma$}

the seal interpretation function $h^\mathrm{code,\square}_\sigma \; (\dots)$ in the code region dictates the return seals and closure seals can be used to seal.

@@

\subsubsection{Value relations}
  \todo[inline]{Do we cut the sealed case of the untrusted value relation?}

>>>>

The seal interpretation function $H^\mathrm{code,\square}_\sigma \; (\dots)$ in the code region dictates the return seals and closure seals can be used to seal.

@@

\subsubsection{Value relations}
The purpose of the value relations is two fold: It relates the words on \srccm{} to the words they correspond to on \trgcm{}, and it defines what pairs of words are safe, i.e.\ are unable to break the guarantees of the capability machines including the LSE and WBCF guaranteed by \srccm{}.
